\obcproc{Adcs}

\Adcs subsystem is capable working in several distinct modes:

\begin{itemize}
    \item Internal Detumbling
    \item Experimental Detumbling
    \item Experimental Sun Pointing
    \item Idle
    \item Disabled
\end{itemize}

In any given time \Adcs subsystem is operating in any of those modes. By default it
is operating in idle mode. \Adcs mode can be switched by using \tcref{Set Adcs Mode}
telecommand.

\subsection{Internal Detumbling Mode}

This is \Imtq builtin mode that works completely autonomously and does not 
require any specific interaction. In this mode \Imtq operates on its own 
it requires only to be communicated at least once every several seconds. 
This mode can be used to stabilize satellite orientation based on the 
Earth's magnetic field. This mode should be used sparingly as it consumes 
a lot of satellite's power. 

\subsection{Experimental Detumbling Mode}

\danger{DO NOT TURN ON THIS MODE}

Experimental detumbling mode is an implementation of a custom detumbling algorithm (B-dot). 
Although the implementation is done it has been since proven that this algorithm is not ready
for any use. It is proven to be unstable when used on real hardware and when run will actually 
cause satellite to start spinning uncontrollably. In case you are still considering enabling 
this algorithm consider this: 
\begin{quote}Every time you think about enabling experimental detumbling mode, the unholy child
weeps the blood of virgins, and Russian hackers pwn your webapp. Enabling experimental detumbling 
summons tainted souls into the realm of the living. PW-Sat 2 and experimental detumbling go 
together like love, marriage, and ritual infanticide. The force of PW-Sat 2 and Experimental 
Detumbling together in the same conceptual space will destroy your mind like so much watery putty.
If you turn on Experimental Detumbling you are giving in to Them and their blasphemous ways which 
doom us all to inhuman toil for the One whose Name cannot be expressed in the Basic Multilingual 
Plane, he comes. PW-Sat-2-plus-experimental-detumbling will liquify the nerves of the sentient 
whilst you observe, your psyche withering in the onslaught of horror. It is too late it is 
too late we cannot be saved the transgression of a child ensures experimental detumbling will 
consume all living tissue (except those tumbling which it cannot, as previously prophesied) 
dear lord help us how can anyone survive this scourge using experimental detumbling on PW-Sat 2 
has doomed humanity to an eternity of dread torture using experimental detumbling establishes 
a breach between this world and the dread realm of corrupt entities a mere glimpse of the world 
of experimental detumbling will instantly transport a OPER's consciousness into a world of 
ceaseless screaming, he comes, the pestilent slithy experimental-detumbling-infection will devour 
satellite systems and existence for all time he comes he comes do not fight he comes, his unholy
radiance destroying all enlightenment, solar array deployment system leaking from your eyes/like 
liquid pain, the song of experimental detumbling will extinguish the voices of mortal man from 
the sphere I can see it can you see it is beautiful the final snuffing of the lies of Man 
ALL IS LOST ALL IS LOST the pony he comes he comes he comes the ichor permeates all MY FACE MY 
FACE oh god no NO NOOO NO stop the angles are not real ZALGO IS TONY THE PONY HE COMES
\end{quote}

\subsection{Experimental Sun Pointing Mode}

\warn{Do not use this mode}

This mode is not operational. It was never done and in its current state it does nothing. 
When \Adcs is switched to this mode it will be effectively in the same state as it would 
be in Idle state.  

\subsection{Idle Mode}

This is default \Adcs subsystem mode. In this mode \Adcs subsystem is not 
doing anything and waits for the commands. 

\subsection{Disabled Mode}

This special mode is used for blocking \Adcs operations all together. When 
\Adcs is switched to this mode is is put into sleep mode in which only a
explicit switch to Idle mode is allowed. This mode can be used for preventing
accidental running \Adcs subsystem in situations in which \Adcs may introduce 
unwanted and potentially harmful interference. This mode can be used to disable 
\Adcs subsystem if it is determined that it has issues. 

\subsection{Recommendations for operation team}
\begin{itemize}
    \item Do not enable experimental modes!
    \item If the satellite is rotating more than 5-6°/s on any axis, the power budget becomes negative. 
    During the mission, assume critical value of 2-3°/s, above which \texttt{BuiltinDetumbling} must be 
    turned on from ground station.
    \item \sads experiment can only be performed if the rotation is not above 1-2°/s on any axis.    
    \item \Adcs subsystem consumes significant amount of power, don't leave turned on longer than necessary.
    \item Use \texttt{Stopped} mode to turn off \Adcs. Don't use \texttt{Disabled} mode.
    \item Changing detumbling state should be reflected in all \Imtq related telemetry sections.
\end{itemize}

\subsection{\Adcs Mode Blocking}

It is possible to permanently block \texttt{Internal Detumbling Mode} and by doing so prevent it from 
being entered or run as long it is blocked. To do so the operator is to send the \tcref{Set Builtin 
Detumbling Block Mask} telecommand with flag indicating whether or not this mode should be blocked 
or unblocked. Once this mode is blocked it cannot be run or entered until it is unblocked. 
This blockade is persisted even over satellite restart therefore blocking this mode should be 
considered and used only as last resort when it is certain that Builtin detumbling mode
is suffering from serious issues.
