\telecommand{EnterIdleState}

\tccategory{D}

\subsection{General description}
\texttt{EnterIdleState} telecommand allows switching COMM to Idle State mode for given time.

In this mode when Transmitter is idle it will continuously transmit Idle Sequence (0x7E) to help the ground receiver to lock.

\faWarning  Leaving satellite in this state too long will discharge battery and may cause transmitter overheating and failure.
\\\\
Success frame indicates that transmitter entered Idle State.

\paragraph{Known issues}
\begin{itemize}
	\item All response error codes return the same value.
\end{itemize}

\paragraph{Side effects}
\begin{itemize}
	\item \faWarning Above nominal power consumption and transmitter heating.
\end{itemize}

\paragraph{Usage limitations}\mbox{}\\ 
This command should not be used when battery level is low.

\paragraph{Recommendations for operation team}
\begin{itemize}
	\item \textbf{Do not} leave Idle State active beyond communication window.
	\item Monitor power usage and transmitter temperature during Idle State.
	\item If possible use repeated \todo{Send Beacon} or \nameref{tc:PingTelecommand} telecommand instead.
\end{itemize}

\subsection{Definition}
\TelecommandApid{EnterIdleState}
\ctor{EnterIdleState}

Parameters: 

\begin{tabular}{r | l | l}
	Argument                    & Size [bits] & Description \\
	\hline
	\texttt{correlation\_id}    & 8 		  &	Correlation ID \\
	\texttt{duration}			& 8 		  & Time in seconds how long COMM should be kept in Idle State
\end{tabular}

\subsection{Responses}

\paragraph{CommSuccessFrame}
\ResponseApid{CommSuccessFrame}
Correlated response frame \texttt{CommSuccessFrame} confirms that telecommand was received COMM entered Idle State.

\paragraph{CommErrorFrame}
\ResponseApid{CommErrorFrame}
Correlated response frame \texttt{CommErrorFrame} represents error. Error code indicates failure reason:

\begin{tabular}{r | l}
	Error code & Value \\
	\hline
	\texttt{0x01} & Malformed (too short) telecommand \\ 
	 			  & Failed to read current time for setting timeout \\
				  & Failed to enter Idle State by COMM
	
\end{tabular}

\subsection{Example usage}
Enter Idle State for 15 seconds, correlation ID = 11
\binaryForm{EnterIdleState(11, 15)}
