\telecommand{Finalize Program Entry}

\tccategory{D}

\subsection{General description}
\texttt{FinalizeProgramEntry} finalizes programming boot table entry.


\paragraph{Known issues}\mbox{}\\ 
\None

\paragraph{Side effects}\mbox{}\\ 
\None

\paragraph{Usage limitations}
\begin{itemize}
	\item This telecommand must be used exactly as described in \nameref{obc:proc:Program upload} procedure.
\end{itemize}

\paragraph{Recommendations for operation team}1
Refer to \nameref{obc:proc:Program upload} procedure for details on uploading new software version.


\subsection{Definition}
\TelecommandApid{FinalizeProgramEntry}
\TelecommandDeclaration{FinalizeProgramEntry}

Parameters: 

\begin{tcarglist}
	\tcarg{entries}{8}{Bitmask indicating boot slots program entry will be finalized}
	\tcarg{length}{32}{Program length}
	\tcarg{expected\_crc}{16}{Expected CRC}
	\tcarg{name}{(variable)}{Program entry description}
\end{tcarglist}


\subsection{Responses}

\paragraph{EntryFinalizeSuccess}
\ResponseApid{EntryFinalizeSuccess}
Response frame \texttt{EntryFinalizeSuccess} indicates successful finalization of program parts. It carries additional values:

\begin{tabular}{r | r | l}
	Field & Size [bits] & Value \\
	\hline
	\texttt{entries} & 8 & Bitmask indicating boot slots program part was written to \\	
	\texttt{crc} & 8 & CRC of finalized part (should match \texttt{expected\_crc} parameter) \\
\end{tabular}

\paragraph{FinalizeEntryMalformedError} \mbox{} \\
%\ResponseApid{FinalizeEntryMalformedError}
\todo{Add FinalizeEntryMalformedError to OBC response frames} \\
Response frame \texttt{FinalizeEntryMalformedError} indicates failure of finalizing program part.
Malformed telecommand (no further information available).

\paragraph{FinalizeEntryWriteError} \mbox{} \\
%\ResponseApid{FinalizeEntryWriteError}
\todo{Add FinalizeEntryWriteError to OBC response frames} \\
Response frame \texttt{FinalizeEntryWriteError} indicates failure of finalizing program part.
Additional fields are contained within this response frame:

\begin{tabular}{r | r | l}
	Field & Size [bits] & Value \\
	\hline
	\texttt{errorCode} & 8 & FlashStatus error code \\
	\texttt{entry} & 8 & Bitmask indicating boot slot in which error occured \\	
\end{tabular}

\paragraph{FinalizeEntryCRCError} \mbox{} \\
%\ResponseApid{FinalizeEntryCRCError}
\todo{Add FinalizeEntryCRCError to OBC response frames} \\
Response frame \texttt{FinalizeEntryCRCError} indicates failure of finalizing program part because of CRC mismatch.
Additional fields are contained within this response frame:

\begin{tabular}{r | r | l}
	Field & Size [bits] & Value \\
	\hline
	\texttt{entry} & 8 & Bitmask indicating boot slot in which error occured \\	
	\texttt{actual\_crc} & 16 & Calculated actual CRC \\
\end{tabular}


\subsection{Example usage}
Finalize program in boot slots 3,4,5, with length 100 bytes, expected CRC 0xB00B, and description "New stuff".
\exampleCall{FinalizeProgramEntry([3,4,5], 0x100, 0xB00B, "New stuff")}
