\telecommand{Reset Transmitter}

\tccategory{PD}

\subsection{General description}
\texttt{ResetTransmitterTelecommand} telecommand allows resetting COMM transmitter. It sends \texttt{Software Reset} command (0xAA) to COMM Transmitter which causes TX MCU to reboot.

\paragraph{Known issues} \mbox{} \\
\None

\paragraph{Side effects}
\begin{itemize}
	\item Resetting transmitter prunes transmitter queue - any waiting frame will be lost.
	\item After sending reset command, OBC will not be able to transmit any frame for short period of time because it takes some time for TX MCU to boot up. 	
\end{itemize}

\paragraph{Usage limitations} \mbox{} \\
Use it only in case of detected malfunction.

\paragraph{Recommendations for operation team}
\begin{itemize}
	\item When OPER detects COMM transmitter malfunction (i.e. uninterrupted carrier wave transmission), then sending \texttt{ResetTransmitterTelecommand} may mitigate this situation.
	\item Because it takes some time for TX MCU to boot, it's possible that after resetting transmitter there will be a temporary spike in error counter values.
	\item OBC has a mechanism to monitor COMM malfunctions. \todo{Link to COMM watchdog}.
\end{itemize}

\subsection{Definition}
\TelecommandApid{ResetTransmitterTelecommand}
\TelecommandDeclaration{ResetTransmitterTelecommand}

Parameters: 

\None

\subsection{Responses}

Since \texttt{ResetTransmitterTelecommand} resets the transmitter, it's unable to send any response. 

\subsection{Example usage}
Reset COMM transmitter.

\exampleCall{ResetTransmitterTelecommand()}