\telecommand{Send Periodic Message}

\tccategory{PD}

\subsection{General description}
\texttt{SendPeriodicMessageTelecommand} sends in response requested number of Periodic Message frames.

By default sending Periodic Message is disabled for power management reasons.

There is no Error Frame in case of errors.

\paragraph{Known issues}
\begin{itemize}
	\item \warn{Requesting more than 40 frames will trigger \nameref{obc:proc:COMM Hang Prevention System} that will cause COMM reset and resetting queue of frames to be send. That may cause communication data loss.}
	\item Operator can request up to 255 periodic frames.
\end{itemize}

\paragraph{Side effects}
\begin{itemize}
	\item Above nominal power consumption and transmitter heating.
\end{itemize}

\paragraph{Usage limitations}\mbox{}\\ 
This command should not be used when battery level is low.

\paragraph{Recommendations for operation team}
\begin{itemize}
	\item \textbf{Do not} request more than 40 frames and be careful when requesting more than 20. You should not hit limit of 40 frames in COMM TX Queue.
	\item Monitor power usage and transmitter temperature during Idle State.
\end{itemize}

\subsection{Definition}
\TelecommandApid{SendPeriodicMessageTelecommand}
\ctor{SendPeriodicMessageTelecommand}

Parameters: 

\begin{tcarglist}
	\tcarg{count}{8}{Number of Periodic Messages to be send}
\end{tcarglist}

\subsection{Responses}

\paragraph{PeriodicMessageFrame}
\ResponseApid{PeriodicMessageFrame}
Correlated response frame \texttt{PeriodicMessageFrame} contains just Periodic message.

Default content is: \\
\texttt{We are the Borg. Lower your shields and surrender your ships. We will add your biological and \\
technological distinctiveness to our own. Your culture will adapt to service us. Resistance is futile.}
Content can be set by \nameref{tc:SetPeriodicMessage}.

\subsection{Example usage}
Send Periodic Message 6 times.
\binaryForm{SendPeriodicMessageTelecommand(6)}
