\telecommand{Set Error Counter Configuration}

\tccategory{PD}

\subsection{General description}
Telecommand for setting Error Counters configuration. See \procref{Error Counters} for detailed discussion about error counters. 

Current configuration can be retrieved using \tcref{Get Error Counter Configuration} telecommand.

\danger Be careful when setting the values, as they can cause OBC to reboot often.

\paragraph{Known issues} \mbox{} \\
\None

\paragraph{Side effects} \mbox{} \\
\None

\paragraph{Usage limitations} \mbox{} \\
\None

\paragraph{Recommendations for operation team} 
\begin{itemize}
	\item Setting the Error Limit lower than Increment will cause the OBC to reboot after each error! Make sure the Error Limit is sufficiently big.
	\item Setting the Increment value to 0 disables the error counter, preventing it to reboot the OBC.
	\item Decrement should not be bigger than Increment. The desired behavior is that lots of error with rare success should still cause OBC reboot. 
\end{itemize}

\subsection{Definition}
\TelecommandApid{SetErrorCounterConfig}
\TelecommandDeclaration{SetErrorCounterConfig}

Parameters:

\begin{tcarglist}
	\tcarg{correlation\_id}{8}{Correlation ID}
	\hline 
	\multicolumn{3}{c}{Following 4 arguments can be repeated for each device id:} \\
	\hline 
	\tcarg{device id}{8}{ID of error counter (see table in \procref{Error Counters})}
	\tcarg{limit}{8}{Error Limit}
	\tcarg{increment}{8}{Value by which counter will be incremented on failure}
    \tcarg{decrement}{8}{Value by which counter will be decremented on success} 
\end{tcarglist}


\subsection{Responses}
\responseFrame{ErrorCounterConfigurationSuccessFrame}
\ResponseApid{ErrorCounterConfigurationSuccessFrame}
Correlated success response frame is of type \texttt{ErrorCounterConfigurationSuccessFrame}. The frame contains additional byte with error counter id for each error counter that has been successfully updated.

\responseFrame{ErrorCounterConfigurationErrorFrame}
\ResponseApid{ErrorCounterConfigurationErrorFrame}

This frame is send only if the OBC failed to read sequence number. In all other cases, the \texttt{ErrorCounterConfigurationSuccessFrame}. Investigate returned device ids to see if they match requested changes.

\subsection{Example usage}
Using correlation id 0x21, for RTC error counter (ID=2), set Error limit to 137, increment to 7, decrement to 3:
\exampleCall{SetErrorCounterConfig(0x21, [telecommand.ErrorCounterConfiguration(2, 137, 7, 3)])}