\telecommand{Set ADCS Mode}

\tccategory{D}

\subsection{General description}
\texttt{SetAdcsMode} telecommand sets new ADCS subystem operating mode. Practically it can either set the Builtin Detumbling (which will turn on the iMTQ module) or disable the ADCS completly. If ADCS is disabled/stopped the ADCS subsystem (iMTQ) will be powered off. Enabling the detumbling will power on the iMTQ.

\paragraph{Known issues}
\begin{itemize}
    \item \danger \texttt{ExperimentalDetumbling} mode's tests have shown that they are unstable.
    DO NOT TURN ON experimental detumbling! It's harmful to satellite's power budget and may cause an overheat!
    \item \danger \texttt{ExperimentalSunpointing} mode has not been implemented. DO NOT TURN ON ADCS experimental sun pointing!
    \item \warn Adcs has two "inactive" modes: \texttt{Stopped} and \texttt{Disabled}. There's almost no difference in effects, both will cause iMTQ to be powered off. However, if satellite is in \texttt{Disabled} mode, then it must first be set to \texttt{Stopped} before enabling detumbling.
\end{itemize}

\paragraph{Side effects} 
\begin{itemize}
    \item Every time you think about enabling experimental detumbling mode, the unholy child weeps the blood of virgins, and Russian hackers pwn your webapp. Enabling experimental detumbling summons tainted souls into the realm of the living. PW-Sat 2 and experimental detumbling go together like love, marriage, and ritual infanticide. The force of PW-Sat 2 and Experimental Detumbling together in the same conceptual space will destroy your mind like so much watery putty. If you turn on Experimental Detumbling you are giving in to Them and their blasphemous ways which doom us all to inhuman toil for the One whose Name cannot be expressed in the Basic Multilingual Plane, he comes. PW-Sat-2-plus-experimental-detumbling will liquify the n​erves of the sentient whilst you observe, your psyche withering in the onslaught of horror. It is too late it is too late we cannot be saved the trangession of a chi͡ld ensures experimental detumbling will consume all living tissue (except those tumbling which it cannot, as previously prophesied) dear lord help us how can anyone survive this scourge using experimental detumbling on PW-Sat 2 has doomed humanity to an eternity of dread torture using experimental detumbling establishes a breach between this world and the dread realm of c͒ͪo͛ͫrrupt entities a mere glimpse of the world of experimental detumbling will ins​tantly transport a OPER's consciousness into a world of ceaseless screaming, he comes, the pestilent slithy experimental-detumbling-infection wil​l devour satellite systems and existence for all time he comes he comes do not fi​ght he com̡e̶s, ̕h̵i​s un̨ho͞ly radiańcé destro҉ying all enli̍̈́̂̈́ghtenment, solar array deployment system lea͠ki̧n͘g fr̶ǫm ̡yo​͟ur eye͢s̸ ̛l̕ik͏e liq​uid pain, the song of experimental detumbling will exti​nguish the voices of mor​tal man from the sp​here I can see it can you see ̲͚̖͔̙î̩́t̲͎̩̱͔́̋̀ it is beautiful t​he final snuffing of the lie​s of Man ALL IS LOŚ͖̩͇̗̪̏̈́T ALL I​S LOST the pon̷y he comes he c̶̮omes he comes the ich​or permeates all MY FACE MY FACE ᵒh god no NO NOO̼O​O NΘ stop the an​*̶͑̾̾​̅ͫ͏̙̤g͇̫͛͆̾ͫ̑͆l͖͉̗̩̳̟̍ͫͥͨe̠̅s ͎a̧͈͖r̽̾̈́͒͑e n​ot rè̑ͧ̌aͨl̘̝̙̃ͤ͂̾̆ ZA̡͊͠͝LGΌ ISͮ̂҉̯͈͕̹̘̱ TO͇̹̺ͅƝ̴ȳ̳ TH̘Ë͖́̉ ͠P̯͍̭O̚​N̐Y̡ H̸̡̪̯ͨ͊̽̅̾̎Ȩ̬̩̾͛ͪ̈́̀́͘ ̶̧̨̱̹̭̯ͧ̾ͬC̷̙̲̝͖ͭ̏ͥͮ͟Oͮ͏̮̪̝͍M̲̖͊̒ͪͩͬ̚̚͜Ȇ̴̟̟͙̞ͩ͌͝S̨̥̫͎̭ͯ̿̔̀ͅ
    \item \texttt{ExperimentalSunpointing} has a major side effect of doing nothing.
\end{itemize}

\paragraph{Usage limitations} \mbox{} \\
Do not turn on experimental modes.

\paragraph{Recommendations for operation team}
\begin{itemize}
    \item Do not enable experimental modes!
    \item If the satellite is rotating more than 5-6°/s on any axis, the power budget becomes negative. During the mission, assume critical value of 2-3°/s, above which \texttt{BuiltinDetumbling} must be turned on from ground station.
    \item SADS experiment can only be performed if the rotation is not above 1-2°/s on any axis.    
    \item ADCS subsystem consumes significant amount of power, don't leave turned on longer than necessary.
    \item Use \texttt{Stopped} mode to turn off ADCS. Don't use \texttt{Disabled} mode.
    \item Changing detumbling state should be reflected in all `Imtq` related telemetry sections.
\end{itemize}

\subsection{Definition}
\TelecommandApid{SetAdcsModeTelecommand}
\TelecommandDeclaration{SetAdcsModeTelecommand}

Parameters: 

\begin{tcarglist}	
	\tcarg{correlation\_id}{8}{Correlation ID}
	\tcarg{mode}{8}{Desired ADCS mode (see table below)}
\end{tcarglist}

Values for \texttt{mode} argument:

\begin{tabular}{r | l}
    Mode & \texttt{mode} value \\
    \hline
    Disabled & -2 \\
    Stopped & -1 \\
    BuiltinDetumbling & 0 \\
    ExperimentalDetumbling & 1 \\
    ExperimentalSunpointing & 2 \\
\end{tabular}


\subsection{Responses}

\paragraph{SetAdcsModeSuccessFrame}
\ResponseApid{SetAdcsModeSuccessFrame}
Correlated response frame \texttt{SetAdcsModeSuccessFrame} confirms that telecommand was received and requested ADCS mode was scheduled.  It DOES NOT mean that setting the mode was successful. This response can be distinguished from \texttt{SetAdcsModeErrorFrame} because the byte after correlation id is set to 0. 

\paragraph{SetAdcsModeErrorFrame}
\ResponseApid{SetAdcsModeErrorFrame}
Correlated response frame \texttt{SetAdcsModeErrorFrame} represents error. This response can be distinguished from \texttt{SetAdcsModeSuccessFrame} because the byte after correlation id is set to 1. There's no additional information about error, the likely causes are invalid request frame or failure to schedule ADCS mode.

\subsection{Example usage}
Enable built-in detumbling, correlation ID = 11.

\exampleCall{SetAdcsModeTelecommand(11, 0)}

Turn ADCS off, correlation ID = 12.

\exampleCall{SetAdcsModeTelecommand(12,-1)}