\telecommand{Set Builtin Detumbling Block Mask}

\tccategory{D}
\subsection{General description}
\texttt{SetBuiltinDetumblingBlockMask} telecommand can be used to enable/disable use of 
\Imtq's builtin detumbling algorithm. Such change is persistent and no satellite reboot 
will change. The block mask is stored in \procref{Persistent State}. The only 
way to undo changes made by this telecommand is to issue it again with appropriate 
block mask.

\paragraph{Known issues} \mbox{} \\
\None

\paragraph{Side effects} \mbox{} \\
\None

\paragraph{Usage limitations} \mbox{} \\
Successful response for this command does not mean that builtin is no longer running. 
This command merely prevents \obc from using it in future. This command will cause \obc
to go out builtin detumbling is it was already active. To to that use \tcref{Set ADCS Mode}.

\paragraph{Recommendations for operation team} \mbox{} \\
This command allows permanent blocking of \Imtq's builtin detumbling. It \textbf{should not} 
be used unless the \Imtq's internal detubmling is known to be no longer working or is causing
problems of any kind. 
Note that when \Imtq's builtin detubmling is blocked it will not be possible to switch 
current \Adcs mode to the builtin detumbing even by using \tcref{Set ADCS Mode} telecommand.

\subsection{Definition}
\TelecommandApid{SetBuiltinDetumblingBlockMaskTelecommand}
\TelecommandDeclaration{SetBuiltinDetumblingBlockMaskTelecommand}

Parameters: 

\begin{tcarglist}
    \tcarg{correlation\_id}{8}{Correlation ID}
    \tcarg{mask}{8}{Builtin detumbling mask. Non zero value block \Imtq's builtin detubmling. Zero unblocks it.}
\end{tcarglist}

\subsection{Responses}
\ResponseApid{SetInternalDetumblingModeSuccessFrame}
\paragraph{SetInternalDetumblingModeSuccessFrame}
Correlated response frame \texttt{SetInternalDetumblingModeSuccessFrame} confirming 
that builtin detumbling mask has been updated.

\paragraph{FileRemoveErrorFrame}
Correlated response frame \texttt{SetInternalDetumblingModeErrorFrame} representing an error. 
Error code indicates failure reason:

\begin{tabular}{r | l}
    Error code & Value \\
    \hline
    \texttt{0x00}   & Success \\
    \texttt{0x01}   & Malformed (too short) telecommand \\
    \texttt{0x02}   & Unable to update detumbling mask in persistent storage \\
\end{tabular}

\subsection{Examples}
Disable builtin detumbling with correlation id set to 10

\exampleCall{SetBuiltinDetumblingBlockMaskTelecommand(10, True)}

