\telecommand{SetPeriodicMessage}

\tccategory{PD}

\subsection{General description}
\texttt{SetPeriodicMessageTelecommand} sets periodic message. Periodic message settings are stored in Persistent State. To retrieve current settings, use \texttt{GetPersistentState} telecommand. 

\paragraph{Known issues} \mbox{} \\
It's not possible to change interval of periodic message without changing its content.

\paragraph{Side effects}
\begin{itemize}
	\item Periodic message is enabled
	\item Increased power usage
\end{itemize}

\paragraph{Usage limitations} \mbox{} \\
Periodic message can cause increased power usage. Before enabling make sure that enough power can be provided.

\paragraph{Recommendations for operation team} \mbox{} \\
Before enabling periodic message make sure that enough power can be provided. \todo{Describe how periodic message affects power usage}.

\subsection{Definition}
\TelecommandApid{SetPeriodicMessageTelecommand}
\TelecommandDeclaration{SetPeriodicMessageTelecommand}

Parameters:

\begin{tcarglist}
	\tcarg{correlation\_id}{8}{Correlation ID}
	\tcarg{interval\_minutes}{8}{Interval between sending messages, in minutes}
	\tcarg{repeat\_count}{8}{Number of messages to send at once}
	\tcarg{message}{max 200 * 8 (String)}{Message payload}
\end{tcarglist}

\subsection{Responses}
\responseFrame{PeriodicSetSuccessFrame}
\ResponseApid{PeriodicSetSuccessFrame}
Correlated success response frame is of type \texttt{PeriodicSetSuccessFrame} is sent after periodic message settings have been saved correctly.

\responseFrame{PeriodicSetErrorFrame}
\ResponseApid{PeriodicSetErrorFrame}
Error frame is of type \texttt{PeriodicSetErrorFrame} and contains error code. 

\begin{tabular}{r | l}
	Error code & Description \\ \hline
	\texttt{0x01} & Malformed (too short) telecommand or empty periodic message
\end{tabular}

\subsubsection{Example usage}
Set periodic message "We are The Borg", sent twice every 5 minutes. Correlation ID = 11:
\exampleCall{SetPeriodicMessageTelecommand(11, 5, 2, "We are The Borg")}
