\responseFrame{Compile Info Response}
\ResponseApid{CompileInfoFrame}

This frame contains full or partial textual description of current \pwsat software version in the following format:\bigskip\\
\texttt{<BUILD_TYPE> Build from '<GIT_COMMIT_HASH>' branch: <GIT_BRANCH>\\ MCU: <TARGET_MCU_PLATFORM>\\Payload: <TARGET_PLD_PLATFORM>\\Machine: <HOST_NAME>\\Built in <BINARY_DIR>\\GCC: <GCC_VERSION>}\bigskip\\
Where:
\begin{itemize}
    \item \texttt{<BUILD_TYPE>} is the name of the current build. It can be either \texttt{Release} or \texttt{Debug}.
    \item \texttt{<GIT_COMMIT_HASH>} is the git commit hash from which currently running OBC software has been built.
    \item \texttt{<TARGET_MCU_PLATFORM>} is the current microcontroller platform name. This can be one of the following: 
        \begin{itemize}
            \item \texttt{EngModel} - for microcontroller engineering model variant,
            \item \texttt{FlightModel} - for microcontroller flight variant,
            \item \texttt{DevBoard} - for evaluation board.
        \end{itemize}
    \item \texttt{<TARGET_PLD_PLATFORM>} is the current payload platform name. This can be one of the following: 
        \begin{itemize}
            \item \texttt{FlightModel} - for payload flight model variant,
            \item \texttt{DM} - for payload mock.
        \end{itemize}
    \item \texttt{<HOST_NAME>} - name of the host machine that produced this \OBC software build.
    \item \texttt{<BINARY_DIR>} - path to the build directory on the current machine.
    \item \texttt{<GCC_VERSION>} - GCC compiler version used to build the \OBC software.
\end{itemize}

In case single \texttt{CompileInfoFrame} will not be able to hold entire version information there the \OBC will split the version information into parts and will send them in separate \texttt{CompileInfoFrame}s each containing subsequent parts of the information string. 